---
title: "Wealth and income"
subtitle: "TidyTuesday 2021 week 07 "
author: "[Camilo Garcia](https://camilogarciabotero.github.io)"
date: "`r format(Sys.time(), '%d %B %Y')`"
mail: "cgarci39@eafit.edu.co"
twitter: "gaspardelanoche"
#orcid: "0000-0002-0426-7007"
github: "camilogarciabotero"
home: "camilogarciabotero.github.io"
coffee: "camilogarciabotero"
#scholar: "OJ6452UAAAAJ&hl"
#researchgate: "Camilo_Garcia-Botero"
#logo: "../img/coffee-4.png"
output:
  epuRate::epurate:
   toc: TRUE
   number_sections: FALSE
   code_folding: "show"
bibliography: ../../bibliography.bib
link-citations: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = " ")
```

```{r libraries, cache = T, include=FALSE, warning=FALSE, message=FALSE}
library(tidyverse) 
library(tidytuesdayR)
library(ggprism)
library(rmarkdown)
library(bookdown)
library(epuRate)
library(knitr)
library(citr)
```

# Data import 

Using the `tidytuesdayR` package this task is easy:

```{r, message=FALSE, warning=FALSE, cache=TRUE}
data <-  tidytuesdayR::tt_load(2021, week = 7)
student_debt <- data$student_debt
```

```{r}
head(student_debt)
```

# Students debts over time

```{r, warning=FALSE, message=FALSE, fig.height= 6, fig.width=8, dpi = 100}

student_debt %>%
  ggplot(aes(year, loan_debt, color = race)) +
  geom_line() +
  eafithemer::theme_eafit_light() +
  eafithemer::scale_color_eafit() +
  theme(
    legend.title = element_blank(),
    axis.line = element_line(color = "#000000"),
    axis.ticks = element_line(color = "#000000"),
    panel.grid = element_line(color = "#DDDDDD", linetype = "dotted") # Soft gray
  ) +
  labs(
    x = "",
    y = "Loan debt (US)"
  ) +
  scale_x_continuous(guide = "prism_offset_minor", limits = c(1990,2015)) +
  scale_y_continuous(guide = "prism_offset_minor", limits = c(1000, 10000)) 

```


***
<br><br>

<div id="disqus_thread"></div>
<script>

/**
*  RECOMMENDED CONFIGURATION VARIABLES: EDIT AND UNCOMMENT THE SECTION BELOW TO INSERT DYNAMIC VALUES FROM YOUR PLATFORM OR CMS.
*  LEARN WHY DEFINING THESE VARIABLES IS IMPORTANT: https://disqus.com/admin/universalcode/#configuration-variables*/
/*
var disqus_config = function () {
this.page.url = PAGE_URL;  // Replace PAGE_URL with your page's canonical URL variable
this.page.identifier = PAGE_IDENTIFIER; // Replace PAGE_IDENTIFIER with your page's unique identifier variable
};
*/
(function() { // DON'T EDIT BELOW THIS LINE
var d = document, s = d.createElement('script');
s.src = 'https://camilogarciabotero-github-io.disqus.com/embed.js';
s.setAttribute('data-timestamp', +new Date());
(d.head || d.body).appendChild(s);
})();
</script>
<noscript>Please enable JavaScript to view the <a href="https://disqus.com/?ref_noscript">comments powered by Disqus.</a></noscript>
***



