---
title: "Astronouts"
subtitle: "TidyTuesday week 29"
author: "[Camilo Garcia](https://camilogarciabotero.github.io)"
date: "`r format(Sys.time(), '%d %B %Y')`"
mail: "cgarci39@eafit.edu.co"
twitter: "gaspardelanoche"
#orcid: "0000-0002-0426-7007"
github: "camilogarciabotero"
home: "camilogarciabotero.github.io"
coffee: "camilogarciabotero"
#scholar: "OJ6452UAAAAJ&hl"
#researchgate: "Camilo_Garcia-Botero"
#logo: "../img/coffee-4.png"
output:
  epuRate::epurate:
   toc: TRUE
   number_sections: FALSE
   code_folding: "show"
bibliography: ../bibliography.bib
link-citations: yes
---

```{r options, include=FALSE}
knitr::opts_chunk$set(cache=TRUE,  comment= " ")
```


```{r libraries, include=FALSE, warning=FALSE, message=FALSE}
library(tidyverse) 
library(tidytuesdayR)
library(hrbrthemes)
library(rmarkdown)
library(bookdown)
library(epuRate)
library(knitr)
library(citr)
library(icon) 
library(gganimate) 
```


<style>
div.red { background-color:#FFE8E8; border-radius: 5px; padding: 30px; } 
div.red p { font-family: Verdana, Geneva, sans-serif; }
</style>
<div class = "red">
<p style="text-align:right">`r icon::fontawesome("r-project")`</p>
**Libraries**
  
  `tidyverse`: data transformations and beautiful plots [@tidyverse2019].<br>
  `hrbrthemes`: this contains the ipsum theme, a very simple and elegant theme [@R-hrbrthemes].<br>
  `rmarkdown`: all the structure of the report relies on this library [@R-rmarkdown].<br>
  `bookdown`: allows the bibliography on the YAML header of this Rmarkdown doc [@bookdown2016; @R-bookdown].<br>
  `epuRate`: the elegant theme of the report [@R-epuRate].<br>
  `knitr`: all parts integration to render the output reporducible report [@knitr2014; @knitr2015; @R-knitr].<br>
  `citr`: addin for easyly find citations in the .bib file and insert in the correct format [@R-citr].<br>
  `icon`: inserting many different icons in markdown [@R-icon].<br>
  `gganimate`: animating ggplot objects [@R-gganimate].

</div>
<br>


<p style="text-align:center">`r icon::fontawesome("rocket", style = "solid")`</p>


# Getting TidyTuesday data

```{r, include=FALSE}
data <-  tidytuesdayR::tt_load(2020, week = 29)
astronauts <- data$astronauts

```

A very handy way to get data from the original TidyTuesday repo is using its own package functions: `data = tidytuesdayR::tt_load(2020, week = 29)` and then we need to store the element of this list as the actual dataset as `astronauts = data$astronauts` so the head looks like:

`r head(astronauts)`
***

Sometimes `head()` function doesn't say to much, so lets use the `glimpse` function of the `{tidyduesdayR}` package to take a good look into the data:

```{r, echo=FALSE}
glimpse(data$astronauts)
```



```{r, eval=FALSE, include=FALSE}


countries <- astronauts %>% 
  select(year_of_mission, total_number_of_missions, nationality) %>%
  group_by(year_of_mission, nationality) %>% 
  mutate(nationality = as_factor(nationality), 
         year_of_mission = as.integer(year_of_mission), 
         ) %>% 
  summarise(
    count = sum(total_number_of_missions)
  ) %>% 
  ungroup() %>% 
  group_by(nationality) %>% 
  mutate(cumsum = cumsum(count)) %>% 
  ungroup() %>% 
  group_by(year_of_mission) %>% 
  mutate(ordering = rank(cumsum, ties.method = "max"))


countries <- astronauts %>% 
  select(year_of_mission, total_number_of_missions, nationality) %>%
  group_by(year_of_mission, nationality) %>% 
  mutate(nationality = as_factor(nationality), 
         year_of_mission = as.integer(year_of_mission)
         ) %>% 
  summarise(
    count = sum(total_number_of_missions),
  ) %>% 
  mutate(ordering = rank(count, ties.method = "max"))



countries <- astronauts %>% 
  select(year_of_mission, total_number_of_missions, nationality) %>% 
  group_by(year_of_mission) %>% 
  mutate(count = sum(total_number_of_missions)) 

  


  summarise(
    count = sum(total_number_of_missions)
  ) %>% 
  ungroup() %>% 
  group_by(nationality) %>% 
  mutate(cumsum = cumsum(count)) %>% 
  ungroup() %>% 
  group_by(year_of_mission) %>% 
  mutate(ordering = rank(cumsum, ties.method = "max")) %>% 
  ungroup()



```




# Astronauts

```{r astronauts, fig.align= "center", fig.height= 18, fig.width=15, dpi = 100, warning=FALSE, message=FALSE, fig.cap= "Fig 1. Comparison of the different coffee ratings for the different cups across countries and its associate distribution coffee cups."}


countries <- astronauts %>% 
  select(year_of_mission, total_number_of_missions, nationality) %>%
  group_by(year_of_mission, nationality) %>% 
  mutate(nationality = as_factor(nationality), 
         year_of_mission = as.integer(year_of_mission), 
         ) %>% 
  summarise(
    count = sum(total_number_of_missions)
  ) %>% 
  ungroup() %>% 
  group_by(nationality) %>% 
  mutate(cumsum = cumsum(count)) %>% 
  ungroup() %>% 
  group_by(year_of_mission) %>% 
  mutate(ordering = rank(cumsum, ties.method = "max")) %>% 
  ungroup()


plot <- countries %>% 
  ggplot(aes(ordering, group = nationality))  +
  geom_tile(aes(y = cumsum/2, 
                height = cumsum,
                width = 0.7), 
            alpha = 0.6) +
  geom_text(aes(y = 0, label = nationality), hjust = 1.1) +
  coord_flip(clip = "off", expand = FALSE) +
  labs(
    title = "{frame_time}",
    subtitle = "",
    y = "Cumulative number of mission per year",
    x = "",
    caption = "Data: TidyTuesday week 29. Plot: @Gaspardelanoche",
    fill = ""
  ) +
  theme_ipsum() +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    plot.subtitle = element_text(size = 18),
    axis.title.x = element_text(size = 18),
    axis.title.y = element_text(size = 18),
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = 14),
    axis.ticks.y = element_blank(),
    plot.caption = element_text(size = 12),
    plot.margin = margin(3, 3, 3, 3, "cm"),
  ) +
  transition_time(year_of_mission) +
  ease_aes('cubic-in') 

animate(plot, nframes = 500, fps = 10, width = 600, height = 600, end_pause = 25)

```

***
<br><br>

<div id="disqus_thread"></div>
<script>

/**
*  RECOMMENDED CONFIGURATION VARIABLES: EDIT AND UNCOMMENT THE SECTION BELOW TO INSERT DYNAMIC VALUES FROM YOUR PLATFORM OR CMS.
*  LEARN WHY DEFINING THESE VARIABLES IS IMPORTANT: https://disqus.com/admin/universalcode/#configuration-variables*/
/*
var disqus_config = function () {
this.page.url = PAGE_URL;  // Replace PAGE_URL with your page's canonical URL variable
this.page.identifier = PAGE_IDENTIFIER; // Replace PAGE_IDENTIFIER with your page's unique identifier variable
};
*/
(function() { // DON'T EDIT BELOW THIS LINE
var d = document, s = d.createElement('script');
s.src = 'https://camilogarciabotero-github-io.disqus.com/embed.js';
s.setAttribute('data-timestamp', +new Date());
(d.head || d.body).appendChild(s);
})();
</script>
<noscript>Please enable JavaScript to view the <a href="https://disqus.com/?ref_noscript">comments powered by Disqus.</a></noscript>


***

# References




